---
title: "ML_Assignment"
author: "Subodh Varkhede"
date: "October 1, 2019"
output: html_document
---

```{r setup, include=FALSE}
library(data.table)
library(dplyr)
library(lubridate)
library(caret)
library(corrplot)
df <- as.data.frame(fread(here::here("pml-training.csv")))
```

## Summary of prediction variable

```{r Summary}
summary(as.factor(df$classe))
```

## Data cleaning

STEP 1 : Remove ~ 100 features from data having more than 19k "NA" values (df_new)
STEP 2 : Remove "Sr","Names", "Time Stamp" variables (df_new_2)

```{r filter_df}

df_new_2 <- df %>% 
  select_if(~sum(!is.na(.)) > 19000) %>%
  select(-c("V1","user_name","raw_timestamp_part_1","raw_timestamp_part_2","cvtd_timestamp"))


glimpse(df_new_2)
  
```


## Train model (Gradient boosting)
I have used "gbm" method from caret package
Accuracy > 99%

Step 1 :  Split Data in Train + Validation (75 / 25)
Step 2 :  Train model ("gbm" in caret)
Step 3:   Check accuracy on Validation set

```{r model}

inTraining <- createDataPartition(df_new_2$classe,p=0.75,list=FALSE)

training <- df_new_2[ inTraining,]
validation  <- df_new_2[-inTraining,]

mod_train <- train(classe~.,method="gbm",data=training,verbose=FALSE)

mod_train
```

## Model accuracy

Model accuracy on validation set is more than 98%

```{r Accuracy}

pred_val <- predict(mod_train,validation)
confusionMatrix (as.factor(pred_val),as.factor(validation$classe))

```
